### 2018-03-13 Paper/jaccardbaetica.tex
updating

@@

All the amphora stamps belong to Dressel 20 types \citep{dressel,martin-kilcher_romischen_1994}. Dressel 20 is commonly associated with transportation of Baetican olive oil through the provinces during the Roman Empire \citep{berni_millet_epigrafianforica_2008}. Most Dressel 20 were marked in stamps and \textit{tituli picti} and inked in graffities with different information but there is not a general consensus about the meaning of them \citep{rodriguez_baetican_1998}. Stamps are the most studied in this type of amphorae. There is evidence that stamps were used for almost three centuries. (economía oleica betica). Frequently, stamps were marked mainly in handles but rarely in rims and body.

@@

However, the 70 \% of stamps cannot be tested due to fragmentation or incomplete information. Consequently, we discard integrate the fragmented stamps in our dataset. We finally filter a total sample of 987 stamps composed by 131 different stamps from 81 workshops.

The chronology in the workshops is widely diverse from the first to the third centuries AD . However, some stamps show a more specific chronology while the majority of them display a large activity of production being difficult to specify an accurate chronology. A reason may be that most of them were partially excavated and only focused on archaeological surveys to collect the maximum stamps as possible (CITAR)

@@

The hypothesis about groups of amphora workshops sharing the same stamps seems not match with the results of analysis even though there are shareable stamps in closer workshops. Probably same stamps detected in closer amphora workshop could have being wrongly catalogued twice in different way in spite of belonging to the same place or being closer between each other.

>>>>

%hablar un poco del comercio del aceite de oliva quizás citando el paper de Williams, Peacok y mattlingly el colega

@@

All the amphora stamps belong to Dressel 20 types \citep{dressel,martin-kilcher_romischen_1994}. Dressel 20 is commonly associated with transportation of Baetican olive oil through the provinces during the Roman Empire \citep{berni_millet_epigrafianforica_2008}. Most Dressel 20 were marked in stamps and \textit{tituli picti} and inked in graffities with different information but there is not a general consensus about the meaning of them \citep{rodriguez_baetican_1998}. Stamps are the most studied in this type of amphorae. There is evidence that stamps were used for almost three centuries. (economía oleica betica). Frequently, stamps were marked mainly in handles but rarely in rims and body \citep{millet_anforas_1998}

@@

However, approximately the 70 \% of stamps cannot be tested due to fragmentation or incomplete information. Consequently, we discard integrate the fragmented stamps in our dataset. We finally filter a total sample of 987 stamps composed by 131 different stamps from 81 workshops.

The chronology in the workshops is widely diverse from the first to the third centuries AD \citep{garcia_vargas_enrique_formal_2010}. However, some stamps show a more specific chronology while the majority of them display a large activity of production being difficult to specify an accurate chronology. A reason may be that most of them were partially excavated and only focused on archaeological surveys to collect the maximum stamps as possible (CITAR)

@@

The hypothesis about groups of amphora workshops sharing the same stamps seems not match with the results of analysis even though there are shareable stamps in closer workshops. Probably same stamps detected in closer amphora workshop could have been wrongly catalogued twice in different way in spite of belonging to the same place or being closer between each other.
